???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-27 article.tex
xgboost edits

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide a both high predictive performance and ability to effectively capture complex relationships. Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees use a given set of data, to predict $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output.

@@

Each function $f_K$ is a classification or regression tree, such that all functions are in defined in the set $\mathcal{F}$ of trees given by ${f(x) = \omega_{q(x)}}(q : \mathbb{R}^m \rightarrow T, \omega \in \mathbb{R}^T)$. Where, $f_K$ corresponds to an independent tree structure $q$ of $\omega$ weights. Each tree has $T$ leaves, which contain a continuous score, represented by $\omega_i$ for the i-th leaf. The final prediction is determined by the sum of the score of the corresponding leaves, given  by $\omega$. The set of functions used by the tree is determined by minimising the regularised objective function, given by:

@@

\par
Chen and Guestrin \citep{chenXGBoostScalableTree2016} further illustrate, using Taylor expansions how, for a fixed structure $q(x)$ the the optimal weight $\omega^*_j$ for a leaf $j$ can be derived. Furthermore they show how to successfully enumarate tree structures using left $I_L$ and right $I_R$ instance sets of nodes and letting $I = I_L \union I_R$. The loss reduction after the split is given by the function:

@@

#
# Connect variable frequency in trees to loss to the objective function.
#

>>>>

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide both a high predictive performance and ability to effectively capture complex relationships. Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output.

@@

Each function $f_K$ is a classification or regression tree, such that all functions are in the set $\mathcal{F}$ of trees given by ${f(x) = \omega_{q(x)}}(q : \mathbb{R}^m \rightarrow T, \omega \in \mathbb{R}^T)$. Where, $f_K$ corresponds to an independent tree structure $q$ of $\omega$ weights. Each tree has $T$ leaves, which contain a continuous score, represented by $\omega_i$ for the i-th leaf. The final prediction is determined by the sum of the score of the corresponding leaves, given  by $\omega$. The set of functions used by the tree is determined by minimising the regularised objective function, given by:

@@

\par
Chen and Guestrin \citep{chenXGBoostScalableTree2016} further illustrate, using Taylor expansions how, for a fixed structure $q(x)$ the the optimal weight $\omega^*_j$ for a leaf $j$ can be derived. Furthermore they show how to successfully enumarate tree structures using left $I_L$ and right $I_R$ instance sets of nodes and letting $I = I_L \cup I_R$. The loss reduction after the split is given by the function:

@@

%
% Connect variable frequency in trees to loss to the objective function.
%
